---
title: "Data Madness"
author: "Martin Gassner, Henry Mauranen, Matteo Maggiolo"
date: "17 March 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
  knitr::opts_chunk$set(
  fig.path = "images/"
)
```


```{r libraries, message=FALSE, warning=FALSE, error=FALSE}
library(Rmisc) # Necessarely before dplyr
library(dplyr)
library(ggplot2)
# library(car)
library(klaR)
library(mclust)
library(stringr)
library(cluster)
library( mice )
library( reshape2 )
library(grDevices)
library( gridExtra )
library( doBy )
```

## Introduction
We worked on a dataset containing the recorded answers to a suvey about morality.

The questions we would like to adress are as follows:

1. Can we find out ways to interpret the answers of each block as one value?

2. Can we identify distinct clusters within different blocks of questions?

3. Based on these values and/or clusters, are there clear correlations between interpretable blocks?

4. Are there interpretable types of individuals?

5. Can we link the clusters to personal metrics?

```{r data_import}
load("./measuringMoralityDuke/MMdata_merged.rdata")
personalColumns <- colnames(MMdata_merged)[255:278]

MMdata_merged[is.na(MMdata_merged)] <- -1

# Leaving out single valued questions, because they can be grouped when constructing the blocks later on
questionIds <- c("C","I","RFQ","REI","MR","EPQ","L","DPES","SP","DIT","RAND_DIT","MELS","MOPS","Dov_mops","MFSS","MI","CQR","IS","SV","TET","EVA")

patternIds <- function( names, pat ) names[ !is.na( str_extract( names, pat ) ) ]

regexes <- sapply(questionIds, function(x){
  paste0("^",x,"[0-9]+(_[A-Z])?$")
  })

questionIdNames <- sapply(regexes, function(x) {
  patternIds(colnames(MMdata_merged), x)
})

block1 <- questionIdNames$C
block2 <- c(questionIdNames$I, questionIdNames$RFQ)
block3 <- questionIdNames$REI
block4 <- c(questionIdNames$MR, questionIdNames$EPQ)
block5 <- questionIdNames$L
block6 <- questionIdNames$DPES
block7 <- c(questionIdNames$DIT, questionIdNames$RAND_DIT)
block8 <- c(questionIdNames$MELS, questionIdNames$MOPS)
block9 <- questionIdNames$MFSS
block10 <- questionIdNames$MI
block11 <- questionIdNames$CQR
block12 <- questionIdNames$IS
block13 <- questionIdNames$SV
block14 <- questionIdNames$TET
block15 <- "Block15"
block16 <- questionIdNames$EVA
block17 <- "Dov_game"

blocks <- list(block1,block2,block3,block4,block5,block6,block7,block8,block9,block10,block11,block12,block13,block14,block15,block16,block17)
```

# EM clustering

The first approach for finding common groups is to cluster the dataset as whole. Here we decided on using EM clustering because of an existing R package. Even though EM is not specifically tailored for catecorigal data, which especially the refusal to answer is, we deemed it suitable. We could also contrast this with kmodes later during the analysis.
A problem with this approach is how to deal with missing values and the mentioned refusals to answer a question. We decided to deal with this by imputing from a column-wise empirical distribution. This way the data set won't enforce existing relations, like imputation by bayesian inference would, and the distribution is maintained, so the mean and variance won't change.

```{r em_clustering}

# Some sections are commented out in this block, as they take a long time to run.


# Imputation with empirical distribution
MMdata.imputed <- MMdata_merged
MMdata.imputed[MMdata.imputed == -1] <- NA
MMdata.imputed[unlist(blocks)] <- apply(MMdata.imputed[unlist(blocks)], 2, function(x){
  na.indecies <- which(is.na(x))
  x[na.indecies] <- mice.impute.sample(x, !is.na(x))
  return(t(x))
})

fullCluster <- Mclust(MMdata.imputed[unlist(blocks)])

MMdata.cluster.variances <- MMdata_merged[unlist(blocks)] %>%
  mutate(classification=fullCluster$classification) %>%
  melt(id=c("classification"))  %>%
  group_by(classification,variable,value) %>%
  count() %>%
  group_by(classification,variable) %>%
  summarise(variance=var(rep(value,n)))

MMdata.cluster.variances.counts <- MMdata.cluster.variances[,-2] %>%
  group_by(classification) %>%
  tally(variance)

MMdata.cluster.variances.counts <- MMdata.cluster.variances.counts[-c(2,3,4,6),]

MMdata.cluster.variances.counts$classification <- as.factor(MMdata.cluster.variances.counts$classification)

ggplot(MMdata.cluster.variances.counts, aes(x=classification, y=n,fill=classification)) + 
  geom_col() +
  ylab( "sums of Var per cluster") +
  ggtitle( "variances per cluster" )

```

After clustering, we observed 8 distinct groups. 4 of these consisted of 4 or fewer individuals, so we decided to focus on the 4 other major clusters. We then plotted the answer frequencies by cluster and question to observe distinctive features from each cluster. Major opinion divider here was religious identity. Observations for the 4 clusters are as follows:

1. Strongly non- or anti-religious. This was visible in all religious questions throughout the questionnaire. Interestingly, when compared to other clusters, this group showed a nearly equal compassion and adherence to ethics (when asked questions about things such as insurance fraud or cheating in an exam) as groups 2 and 3. This group showed some degree of preference towards moral relativism than other groups.

2. Strongly religious group. Similar to group 3, this group considers religion very important. To contrast, they are more relativistic about morals than group 3 and they tended to answer slightly weaker agreement within questions about sacredness of moral values.

3. Strongly religious group. As hilighted by cluster 2, this group appeared to be a more strict group of religious individuals than group 2.

4. Normal group. This group tended to answer neither agree or disagree for most of the questions, especially the ones about identity. They aren't characterized by any specific question in the entire questionnaire and won't stand out compared to the other 3 groups. However, the interesting observation was that this group considers moral questions, such as the ones in every day moralism section, more loosely than other groups. Their answers didn't show as uniform agreement about immoralities of things like lying or fraud as other groups did.

Finally, we were interested if some of the groups are more uniform in their values than other groups. We summed up variances from each question, producing the plot dispalyed after em_clustering block. The differences in variances are very small and practically insignificant. This is quite surprising as it could be epected that religious groups in USA, being mainly christian, would have a more uniform set of moral principles.

# PCA weighting + kmeans

To obtain a weighting for each block of questions

1. obtain the principal components for each block

2. keep the ones explaining 85% of the variance

3. for each variable: sum the loadings of the most important principal components, 
weighted by the variance explained.

Additionally we tested the weights for significance within each block.

```{r principal_component_analysis}
MMdata_merged.zerofill <- MMdata_merged
MMdata_merged.zerofill[ is.na( MMdata_merged ) ] <- 0
MMdata_merged.zerofill[ MMdata_merged.zerofill == -1 ] <- 0
blocks.pcs <- lapply( blocks, function( b ) princomp( MMdata_merged.zerofill[ b ] ) )

# compute weights from pc
weightsFromPc <- function( t, pc ) 
  {
    parvs <- pc$sdev / sum( pc$sdev )
    cumvs <- cumsum( parvs )
    sigCs <- cumvs < t
    if( length( parvs[ sigCs ] ) > 1 )
      return( apply( abs( parvs[ sigCs ] * pc$loadings[ ,sigCs ] ), 1, sum) )
    else
      return( sum( pc$loadings) )
  }
blocks.weights.raw <- sapply( blocks.pcs, function( pc ) weightsFromPc( 0.85, pc ) )
blocks.weights.norm <- sapply( blocks.weights.raw, function( ws ) ws / sum( ws ) )

# test weights for significance for normal or uniform distributions
# H0: data is normal
testNorm <- function( xs ) if( length( xs ) > 2 ) shapiro.test( xs )$p.value else 0
# H0: data is uniform
testUnif <- function( xs ) ks.test( xs, "punif" )$p.value
# p value of x given that xs if normally distributed
normSig <- function( x, xs ) pnorm( x, mean=mean( xs ), sd=sd( xs ) )
# p value given that x is uniformly distributed
unifSig <- function( x, xs ) x / ( max( xs ) - min( xs ) )
# test whether p lies outside center 1-alpha prob region
twoSideP <- function( alpha, p ) p >= 0 && (p < alpha / 2 || p > 1 - alpha / 2)

alpha <- 0.1

blocks.weights.norm.pnorm <- sapply( blocks.weights.norm, testNorm )
blocks.weights.norm.punif <- sapply( blocks.weights.norm, testUnif )

blocks.weights.norm.sig <- sapply( blocks.weights.norm, function( ws ) replicate( length( ws ), -1 ) )
blocks.weights.norm.sig[ blocks.weights.norm.pnorm > 1 - alpha ] <- sapply( 
  blocks.weights.norm[ blocks.weights.norm.pnorm > 1 - alpha ]
  , function( xs ) sapply( xs, function( x ) normSig( x, xs ) )
  )

blocks.weights.norm.df <- as.data.frame( melt( blocks.weights.norm ) )
blocks.weights.norm.df$name <- unlist( blocks )
blocks.weights.norm.df$sig <- sapply( melt( blocks.weights.norm.sig )$value
                                      , function( pval ) twoSideP( alpha=alpha, pval ) )
ggplot( blocks.weights.norm.df[ blocks.weights.norm.df$L1 != c(15, 17), ]
        , aes( x=name, y=value, color=sig ) ) + 
  geom_col() + 
  facet_wrap( ~L1, ncol=4, scales="free" ) +
  theme( axis.text.x=element_text( angle=45, hjust=1 ) )
```


```{r pca_cmp_threshold}
blocks.altweights.raw <- sapply( blocks.pcs, function( pc ) weightsFromPc( 0.50, pc ) )
blocks.altweights.norm <- sapply( blocks.weights.raw, function( ws ) ws / sum( ws ) )

blocks.altweights.norm.pnorm <- sapply( blocks.altweights.norm, testNorm )
blocks.altweights.norm.punif <- sapply( blocks.altweights.norm, testUnif )

blocks.altweights.norm.sig <- sapply( blocks.altweights.norm, function( ws ) replicate( length( ws ), -1 ) )
blocks.altweights.norm.sig[ blocks.altweights.norm.pnorm > 1 - alpha ] <- sapply( 
  blocks.altweights.norm[ blocks.altweights.norm.pnorm > 1 - alpha ]
  , function( xs ) sapply( xs, function( x ) normSig( x, xs ) )
  )

blocks.altweights.norm.df <- as.data.frame( melt( blocks.weights.norm ) )
blocks.altweights.norm.df$name <- unlist( blocks )
blocks.altweights.norm.df$sig <- sapply( melt( blocks.altweights.norm.sig )$value
                                      , function( pval ) twoSideP( alpha=alpha, pval ) )

ggplot( blocks.weights.norm.df[ blocks.weights.norm.df$L1 != c(15, 17), ]
        , aes( x=name, y=value, color=sig ) ) + 
  geom_col() + 
  facet_wrap( ~L1, ncol=4, scales="free" ) +
  theme( axis.text.x=element_text( angle=45, hjust=1 ) )
```


```{r transforming_blocks}
# just do matrix multiply: original dims x reduced dims
blockTransform <- matrix( data=0, nrow=length( unlist( blocks ) ), ncol=length( blocks ) )
for( ib in 1:length( blocks ) )
{
  off <- if( ib > 1 ) sum( sapply( blocks, length )[ 1:(ib - 1) ] ) else 0
  blockTransform[ (off + 1):(off + length( blocks[[ ib ]] ) ), ib ] <- blocks.weights.norm[[ ib ]]
}
```


```{r clustering_transformed_blocks}
MMdata.blockt <- as.matrix( MMdata_merged[ ,unlist( blocks ) ] ) %*% blockTransform
MMdata.blockt.kclusters <- lapply( 2:20, function( k ) kmeans( MMdata.blockt
                                                               , centers=unique( MMdata.blockt )[ 1:k, ]
                                                               , iter.max=100 )  )

weightedIntradiff <- function( k ) sum( k$withinss * k$size )
plot( sapply( MMdata.blockt.kclusters, weightedIntradiff )
      , xlab="number of clusters"
      , ylab="weighted intraclass difference" 
      , main="difference per cluster size")

diff1d2pt <- function( xl, xm, h ) (xl - xm) / h
diff2d3pt <- function( xl, xm, xr, h ) (xl - 2*xm + xr) / h^2
```

```{r clustering_transformed_sizes}
transformClusterSize <- 5
MMdata.blockt.clustered <- data.frame( cbind( MMdata.blockt
                                              , factor( MMdata.blockt.kclusters[[ transformClusterSize - 1 ]]$cluster ) ) )
colnames( MMdata.blockt.clustered ) <- c( paste0( "block", 1:length( blocks ) ), "cluster" )

# use this if NOT knitting
# MMdata.blockt.clustered.counts <- data.frame( count( MMdata.blockt.clustered$cluster ) )
# use this if knitting
MMdata.blockt.clustered.counts <- data.frame( count( MMdata.blockt.clustered, cluster ) )

#ggplot( MMdata.blockt.clustered.counts
#        , aes( x=x, y=freq ) ) + geom_col() +
#  xlab( "cluster" ) + ylab( "size" ) + ggtitle( "cluster sizes" )
```


```{r clustering_transformed}


ggplot( melt( MMdata.blockt.clustered, id.vars="cluster")
        , aes( group=cluster, x=cluster, y=value ) ) + 
  geom_boxplot() + 
  facet_wrap( ~variable, scales="free_y" ) +
  ggtitle( "distribution of responses" )
```


```{r transformed_cluster_lines}
MMdata.blockt.clustered.rawmeans <- lapplyBy( ~cluster
                                              , data=MMdata.blockt.clustered
                                              , FUN=colMeans )
MMdata.blockt.clustered.means <- melt( matrix( unlist( 
  MMdata.blockt.clustered.rawmeans[ order( names( MMdata.blockt.clustered.rawmeans ) ) ] )
  , ncol=length( MMdata.blockt.clustered.rawmeans ) ) )
colnames( MMdata.blockt.clustered.means ) <- c( "block", "cluster", "mean" )
MMdata.blockt.clustered.means$cluster <- factor( MMdata.blockt.clustered.means$cluster )
ggplot( MMdata.blockt.clustered.means
        , aes( x=block, y=mean, color=cluster ) ) +
  geom_line() +
  xlab( "question block" ) + ylab( "mean response" ) +
  ggtitle( "Overview of mean responses" )
```

big differences
Block 2: Identity measures - clusters 2,5 (less important) vs. 1,3 (very important)

highly weighted: job, political party, favorite sports team

Block 4: Moral relativism - cluster 2 (relative) vs 5 (disagreeing)

higly weighted: What is right and wrong is up to each person to decide

Block 9: Sacredness of moral principles - cluster 1 (less) vs 2,3,5 (more)

higly weighted: Sign a piece of paper that says “I hereby sell my soul, after my death, to whoever has
this piece of paper” (SIGNIFICANT)

low weighted: Attend a performance art piece in which all participants (including you) have to act
like animals for 30 minutes, including crawling around naked and urinating on stage

Block 17: all different; rank 1, 2, 3, 4, 5

```{r transformed_cluster_significance}
print( "Block 2: Identity measures - clusters 2,5 (less important) vs. 1,3 (very important)" )
t.test( MMdata.blockt.clustered$block4[ is.element( MMdata.blockt.clustered$cluster, c(2,5) ) ]
        , MMdata.blockt.clustered$block4[ is.element( MMdata.blockt.clustered$cluster, c(1,3) ) ] )$p.value

print( "Block 4: Moral relativism - cluster 2 (relative) vs 5 (disagreeing)" )
t.test( MMdata.blockt.clustered$block4[ is.element( MMdata.blockt.clustered$cluster, c(2) ) ]
        , MMdata.blockt.clustered$block4[ is.element( MMdata.blockt.clustered$cluster, c(5) ) ] )$p.value

print( "Block 9: Sacredness of moral principles - cluster 1 (less) vs 2,3,5 (more)" )
t.test( MMdata.blockt.clustered$block4[ is.element( MMdata.blockt.clustered$cluster, c(1) ) ]
        , MMdata.blockt.clustered$block4[ is.element( MMdata.blockt.clustered$cluster, c(2,3,5) ) ] )$p.value

print("Block 17: Dictator game - cluster 1 vs 2, 3, 4, 5")
t.test( MMdata.blockt.clustered$block4[ is.element( MMdata.blockt.clustered$cluster, c(1) ) ]
        , MMdata.blockt.clustered$block4[ is.element( MMdata.blockt.clustered$cluster, c(2,3,4,5) ) ] )$p.value

print("Block 17: Dictator game - cluster 2 vs 1, 3, 4, 5")
t.test( MMdata.blockt.clustered$block4[ is.element( MMdata.blockt.clustered$cluster, c(2) ) ]
        , MMdata.blockt.clustered$block4[ is.element( MMdata.blockt.clustered$cluster, c(1,3,4,5) ) ] )$p.value

print("Block 17: Dictator game - cluster 3 vs 1, 2, 4, 5")
t.test( MMdata.blockt.clustered$block4[ is.element( MMdata.blockt.clustered$cluster, c(3) ) ]
        , MMdata.blockt.clustered$block4[ is.element( MMdata.blockt.clustered$cluster, c(1,2,4,5) ) ] )$p.value

print("Block 17: Dictator game - cluster 4 vs 1, 2, 3, 5")
t.test( MMdata.blockt.clustered$block4[ is.element( MMdata.blockt.clustered$cluster, c(4) ) ]
        , MMdata.blockt.clustered$block4[ is.element( MMdata.blockt.clustered$cluster, c(1,2,3,5) ) ] )$p.value

print("Block 17: Dictator game - cluster 5 vs 1, 2, 3, 4")
t.test( MMdata.blockt.clustered$block4[ is.element( MMdata.blockt.clustered$cluster, c(5) ) ]
        , MMdata.blockt.clustered$block4[ is.element( MMdata.blockt.clustered$cluster, c(1,2,3,4) ) ] )$p.value

```

Cluster 1

- find many things (country, religion etc) relevant to their identity

- do not hold moral values high/more pragmatic

- give the least in the dictator game

Cluster 2

- find less things relevant to their identity

- moral relativists

- do think of their moral values sacred/would take a lot of money

- second to last in dictator game

Cluster 3

- average, really everywhere

Cluster 4 

- irrelevant, too small, collects refused answers

Cluster 5

- find less things relevant to their identity

- oppose moral relativism

- do hold their morals dear

- give the most in the dictator game (exactly average)

```{r clustering_transformed_personal}
# means of personal variables
MMdata.merged.clustered <- cbind( MMdata_merged, MMdata.blockt.clustered$cluster )
colnames( MMdata.merged.clustered ) <- c( colnames( MMdata_merged) , "cluster" )

# MMdata.merged.clustered %>% group_by( cluster ) %>% summarise_at( vars( ppeduc, ppage, ppgender, ppethm, ppincimp, ppnet ), funs( mean( ., na.rm=TRUE)))

MMdata.merged.clustered$ppgender <- factor( MMdata.merged.clustered$ppgender
                                            , labels=c("male", "female" ) )
MMdata.merged.clustered$ppeducat <- factor( MMdata.merged.clustered$ppeducat
                                            , labels=c( "none", "high school", "college", "Bachelors+") )
MMdata.merged.clustered$ppethm <- factor( MMdata.merged.clustered$ppethm
                                          , labels=c( "white", "black", "other", "hispanic", "2+" ) )
#MMdata.merged.clustered$ppincimp <- factor( MMdata.merged.clustered$ppincimp
#                                            , labels=c("< 10k", "10-25k", "25-50k", "50-75k", "75k+" ) )
MMdata.merged.clustered$ppnet <- factor( MMdata.merged.clustered$ppnet
                                         , labels=c( "yes", "no" ) )
MMdata.merged.clustered$ppagect4 <- factor( MMdata.merged.clustered$ppagect4
                                            , labels=c( "18 - 29", "30 - 44", "45 - 59", "60+") )
MMdata.merged.clustered$ppmarit <- factor( MMdata.merged.clustered$ppmarit
                                           , labels=c( "married", "widowed", "divorced", "separated", "never married", "with partner" ) )
MMdata.merged.clustered$pphouse <- factor( MMdata.merged.clustered$pphouse
                                           , labels=c( "house det", "house att", "appartment", "mob home", "other" ) )

pvars.plots <- lapply( c( "ppagect4", "ppeducat", "ppgender", "ppethm", "ppnet", "ppmarit", "pphouse" )
                       , function( v ) ggplot( data=MMdata.merged.clustered
                                               , aes_string( x="cluster", fill=v ) ) +
                         geom_bar( position="fill" ) )

#for( plot in pvars.plots ) plot
grid.arrange( grobs=pvars.plots[ 1:4 ] )
grid.arrange( grobs=pvars.plots[ 5:7 ], ncol=2 ) 

```

# k-modes

```{r kmodes_methods}
# Define methods for the clusters

get_tot_diffs <- function(x, max_size=15) {
  # Get the maximum difference for 15 different cluster sizes (from 2 to 16)
  kmode_res <- lapply(1:max_size, function(i){kmodes(x, i+1)})
  diffs <- lapply(kmode_res, function(y){sum(y$withindiff)})
  return(unlist(diffs))
}

test_kmodes_runs <- function(x, tests=5, max_size=15) {
  # Runs the get_max_diffs function different times to average out the random initial seed of kmodes
  all_tests <- lapply(1:tests, function(y) {get_tot_diffs(x, max_size)})
  
  # Returns dataframe with runs as rows and cluster number as columns (V[number of clusters - 1])
  return(as.data.frame(do.call(rbind, all_tests)))
}

avg_diffs_for_block <- function(x, tests = 20, max_size=15) {
  # Averages the cluster scores given by the previous method
  run_for_block <- test_kmodes_runs(x, tests = tests, max_size = max_size)
  print('Finished testing for one block')
  return(sapply(names(run_for_block), function(y) {mean(run_for_block[,y])}))
}
```

```{r kmodes_on_blocks_init}
multi.dim.idx <- c(1:14,16)
multi.dim.blocks <- blocks[multi.dim.idx]
```

```{r kmodes_on_blocks, eval=FALSE, echo=FALSE}
# WARNING: VERY LONG COMPUTATION! NOT WORTH RUNNING
# The results are in the object n_clust (2 blocks below)
# Actual computation of average intr-cluster difference for different k with kmodes 
all_avgs <- vector('list', length(multi.dim.blocks))
for (i in 1:length(multi.dim.blocks)){
  print(paste0(c('Iteration ', i), collapse = ''))
  
  all_avgs[[i]] <- avg_diffs_for_block(MMdata_merged[,multi.dim.blocks[[i]]], tests = 8)
}
```

```{r print_kmodes, eval=FALSE, echo=FALSE}
for (i in c(1:11,13,14,16)){
  print(paste0(c('Block ', i), collapse=''))
  plot(all_avgs[[i]])
}
```

```{r create_clusters}
# For block 2, 13 and 16 no proper value
# Same order as multi dim blocks
n_clust <- c(6, 4, 5, 6, 5, 6, 7, 7, 6, 6, 7, 8, 5, 8, 9)
clust_obj <- vector('list', length(n_clust))

# Get the cluster objects for each block
for (i in 1:length(multi.dim.blocks)){
  data <- MMdata_merged[,multi.dim.blocks[[i]]]
  clust_obj[[i]] <- kmodes(data, distinct(data[1:n_clust[i],]))
}
all_var_kmodes_6 <- kmodes(MMdata_merged[, unlist(blocks)], distinct(MMdata_merged[1:6,unlist(blocks)]))
all_var_kmodes_9 <- kmodes(MMdata_merged[, unlist(blocks)], distinct(MMdata_merged[1:9,unlist(blocks)]))
all_var_kmodes_11 <- kmodes(MMdata_merged[, unlist(blocks)], distinct(MMdata_merged[1:11,unlist(blocks)]))

clust_df <- data.frame(block1=clust_obj[[1]]$cluster)
for (i in 2:length(multi.dim.blocks)){
  clust_df <- cbind(clust_df, clust_obj[[i]]$cluster)
}
colnames(clust_df) <- paste0('block',multi.dim.idx)

clust_df$all.blocks.6 <- all_var_kmodes_6$cluster
clust_df$all.blocks.9 <- all_var_kmodes_9$cluster
clust_df$all.blocks.11 <- all_var_kmodes_11$cluster
```

```{r, clust_transition_function}
# E.g. create.intersect.df('block1', 'block12', clust_df)
# Given names of 2 columns as string (e.g. block names), a dataframe with cluster values, create heatplot and return matrix
create.intersect.df <- function(x_name,y_name,data,norm_first=TRUE, return_mat=FALSE){
  idx <- data[,x_name]
  idy <- data[,y_name]
  
  # Get the clusters
  clust_x <- lapply(1:max(idx), function(i) which(idx == i))
  clust_y <- lapply(1:max(idy), function(i) which(idy == i))
  
  # Create the matrix with transitions
  mat.res <- lapply(clust_x, function(i) lapply(clust_y, function(j)length(intersect(i,j))))
  mat.res <- t(matrix(unlist(mat.res), nrow = max(idy), ncol = max(idx)))
  
  if (norm_first==TRUE) {
    mat.res <- t(apply(mat.res, 1, function(x) x/sum(x)))
  }
    
  p <- ggplot(melt(mat.res), aes(x=Var1, y=Var2, fill=value)) + geom_tile() + labs(fill='Intersecting', x=paste0(c('from', x_name), collapse = ' '), y=paste0(c('to', y_name), collapse = ' ')) + ggtitle(paste0(c('Transitions from', x_name, 'to', y_name), collapse = ' ')) + geom_text(aes(label=round(value, 3)))
  
  if (return_mat)
    return(mat.res)
  
  return(p)
}
```

```{r transition_graph_list}
block.names <- c("block1", "block2", "block3", "block4", "block5", "block6", "block7", "block8", "block9", "block10", "block11", "block12", "block13", "block14", "block16", 'all.blocks.6', 'all.blocks.9', 'all.blocks.11')

# The list with all transition graphs
graph_list <- vector('list', length(block.names)^2 - length(block.names))
mat_list <- vector('list', length(block.names)^2 - length(block.names))

count <- 1
for (i in 1:length(block.names)){
  for (j in 1:length(block.names)){
    name_1 <- block.names[i]
    name_2 <- block.names[j]
    # Don't get useless identity graphs
    if (name_1 != name_2) {
      graph_list[[count]] <- create.intersect.df(name_1, name_2, clust_df)
      mat_list[[count]] <- create.intersect.df(name_1, name_2, clust_df, norm_first = FALSE, return_mat = TRUE)
      count <- count + 1
    }
  }
}

```

```{r}
plot.clust.distr <- function(clust_name){
  vars <- c('ppagect4', 'ppeducat', 'ppgender', 'ppethm')
  
  agecat <- c('18-29', '30-44', '45-59', '60+')
  educat <- c('Less than HighSchool', 'HighSchool', 'College', 'Bachelor or +')
  gencat <- c('M', 'F')
  ethcat <- c('White', 'Black', 'Other', '2 or more', 'Hispanic')
  
  categories <- list(agecat, educat, gencat, ethcat)
  
  comparison_df <- clust_df
  
  for (i in 1:length(vars)){
    var <- vars[i]
    comparison_df[[var]] <- categories[[i]][MMdata_merged[, var]]
  }
  
  return(multiplot(plotlist=lapply(vars, function(var) ggplot(data=comparison_df, aes_string(x=clust_name, fill=var)) + geom_bar(position='fill')), cols = 2))
}
```


```{r between_clust_analisys}


p_1 <- create.intersect.df('block6', 'block13', clust_df, norm_first = FALSE)
p_2 <- create.intersect.df('block13', 'block16', clust_df, norm_first = FALSE)
p_3 <- create.intersect.df('block6', 'block16', clust_df, norm_first = FALSE)
multiplot(p_1, p_2, p_3, cols = 2)
print("Interesting transition from block6(2) to block13(3), from block16(2) [The 'hippies' (all 7 in block6)]")

plot.clust.distr('block6')
print("Plotting only block 6 info [check cluster 2]")

g_1 <- create.intersect.df('block5', 'block4', clust_df, norm_first = FALSE)
g_2 <- create.intersect.df('block12', 'block4', clust_df, norm_first = FALSE)
g_3 <- create.intersect.df('block10', 'block4', clust_df, norm_first = FALSE)
multiplot(g_1, g_2, g_3, cols = 2)
print("Interesting transition from block5(5) to block4(5), block12(5) to block4(5), block10(5) to block4(5) [Still undecided]")

plot.clust.distr('block5')
print("Plotting only block 5 info [check cluster 5]")

create.intersect.df('block4', 'block12', clust_df, norm_first = FALSE)
print("Interesting transition between block4(1), block12(1) [The 'Believe in Jesus but don't like the word religious'] [about 180 people in both cluster]")

print("Plotting only block 4 info [check cluster 1]")
plot.clust.distr('block4')

create.intersect.df('block16', 'block2', clust_df, norm_first = FALSE)
print("Interesting transition from block16(2) and block2(2) [The non religious] [about 275 people in both clusters]")

plot.clust.distr('block16')
print("Plotting only block 16 info [check cluster 2]")

create.intersect.df('block16', 'block12', clust_df, norm_first = FALSE)
print("Interesting transition between block16(3) and block12(1) [High integrity and moral values (christians)] [about 270 people]")

plot.clust.distr('block12')
print("Plotting only block 12 info [check cluster 6]")

plot.clust.distr('all.blocks.6')
print("Clusters in all.blocks.6 => {6: [Non religious], 4: [Hippies/High integrity and moral], 1: [Always undecided], }")
```

# Conclusions

1. Can we find out ways to interpret the answers of each block as one value?

Yes we can! We used PCA to obtain weights from the sum of loadings per variable weighted by the variance explained by each principal component.

2. Can we identify distinct clusters within different blocks of questions?

Yes we can! We performed k-modes clustering on a per block basis and obtained the cetroids of each cluster. We then related the results with the questions presented in the questionnaire.

3. Based on these values and/or clusters, are there clear correlations between interpretable blocks?

Sometimes. Our results show that the correlations between variables are not particularly strong. However we could find correlations between individual clusters for specific blocks. Additionally, there was often overlap between the clusters and only few variables clearly separated a cluster from the others.

4. Are there interpretable types of individuals?

Based on the per-block basis clustering we could find pairs of clusters correlated over multiple blocks. This established a link between blocks of questions for a specific cluster, such as:

- a group of individuals never taking a side

- a group of individuals with high answers to integrity and ethical values questions

Given our clustering on the entire dataset we could find 4 types

- Materialistic pragmatists

- Individualists

- Average people

- Saints

- Can we link the clusters to personal metrics?

Yes, we can! Corresponding to the previous 4 types

- Materialistic pragmatists

  + mostly young
  
  + educated
  
  + male
  
  + abstain from marriage

- Individualists

  + ethnically more diverse
  
  + less tertiary education
  
  + fewer living in detached houses

- Average people
  
  + guess what... average - everywhere!

- Saints
  
  + most likely to be married
  
  + least likely to have an appartment
  
  + most likely to be living in detached houses
  
  + more women
